Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved by tbm, patterns for metallica mixed with vega pattern
improved

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm,algorithmic}
\usepackage{subfloat,subfig}

@@

Large-scale \cite{Bertin-Mahieux2008}

@@

\section{Experiments - Fundamentals}\label{sec:experiments}
In this section we assert the basic properties of our encoding scheme.
The first subsection gives the details to reproduce the experiments,
such as the distance measure and learning rate. In second subsection, we
measure properties such as ``how the number of codes affect the distortion''
and ``how many learning samples should we use''. Though important numbers
to report, the busy reader could skip to subsection \ref{ssec:random}
and the following sections.
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{code_variance}
\end{center}
\caption{\small{Average variance in time of a codebook.}}
\label{fig:code_var}
\end{figure}

@@

\subsection{Artist Recognition}
Let us be clear, the clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be usefull. However, we can
imagine that some artist use more often some patterns than others.
Best accuracy reported is around $54.5\%$. Our result is $23.4\%$. Random
is around $5\%$. The confusion matrix can be seen in Figure \ref{fig:conf_mat}.
Details of the experiment follow.

>>>>

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm,algorithmic}

% added by tbm
\usepackage{subfloat,subfig}
\setlength{\abovecaptionskip}{-3pt}
\setlength{\belowcaptionskip}{10pt}

@@

Large-scale \cite{Bertin-Mahieux2008}. See previous work for \textit{Shingles}
papers.

@@

\section{Experiments - Fundamentals}\label{sec:experiments}
In this section we assert the basic properties of our encoding scheme.
The first subsection gives the details to reproduce the experiments,
such as the distance measure and learning rate. In the second subsection, we
measure properties such as ``how the number of codes affect the distortion''
and ``how many learning samples should we use''. Though important numbers
to report, the busy reader could skip to subsection \ref{ssec:random}
and the following sections.
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{code_variance}
\end{center}
\caption{\small{Average variance in time of a codebook. The vertical
axis cuts at the $63$rd pattern, a rough estimate of the number of 
sustained note patterns.
}}
\label{fig:code_var}
\end{figure}

@@

\subsection{Artist Recognition}
Let us be clear, the clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be usefull. However, we can
imagine that some artist use more often some patterns than others.
Best accuracy reported\footnote{few details given to preserve anonymity} 
is around $54.5\%$. Our result is $23.4\%$. Random
is around $5\%$. The confusion matrix can be seen in Figure \ref{fig:conf_mat}.
Details of the experiment follow.
